NIRCam Calibration Plan

### 2016-12-13 ms.tex
I re-organized repeat text about the flux ladder.

There are several ways to improve saturation limits with NIRCam:
\begin{itemize}
\item \textbf{Lyot Stop} Cut down the aperture size with a Lyot stop. These have 19\% throughput (1.8 mags). Additionally, this broadens the PSF - see Figure \ref{fig:psfComparison}.
The broadening spreads light out by a similar factor (1.8 mags) for a total of 3.5 mags.
\item \textbf{Neutral Density Square} The neutral density filters have an attenuation of around 10$^3$ or 7.5 mags. A color correction would have to be applied for the neutral density filter (since it is wavelength dependent) when transferring to an un-occulted region.
Additionally, the Lyot stop that must be in place to use the neutral density filter so the total improvement is 11 mags over direct imaging.
Care must be taken with dithering to ensure that non-uniform optical depth of the neutral density filter doesn't affect the photometry.
\item \textbf{Grisms} For long wavelength observations, one can use grism to spread out the light. This mode still has a saturation limit of $K$=4.6 to 3.5 for the F322W2  filter \citep{greene2016wfss}, which does not reach to the MSX standards. This could be potentially combined with the coronagraph, but both at once hasn't been explored much. One could potentially observe small pieces of the spectrum at a time with a subarray that moves along the spectrum, but this would likely be harder to implement.
\item \textbf{DHS} The dispersed Hartmann Sensor (DHS) reduces the pupil throughput and spreads the light out to reach saturation limits of $K$=0.2 to 1.5 depending on spectral type \citep{schlawin2017dhs}. This would also have to be read out with a moving subarray to observe the MSX stars.
\item Use a narrowband filter, such as F121N
\item Use a small subarray - 64 $\times$ 64 is supported for science. There will be an engineering jitter monitoring test with an 8 $\times$ 8 subarray 
\item \textbf{Weak Lens} The Weak Lenses spread light out over many pixels which can be helpful for bright stars. However, one needs to read out larger sized subarrays to encompass the entire hexagonal PSF so this somewhat cancels out.
\end{itemize}

Of the many options here, the most feasible method is the neutral density square with the Lyot Coronagraphic pupil mask.

Sensitivity and saturation limits make use of \texttt{pysynphot} \citep{lim2015pysynphot} with Phoenix stellar models \citep{allard2012phoenix} ranging from 4.0 to 5.0 in log(g).

@@

Figure \ref{fig:msxNCfilterOverlap} shows the MSX filters B1 and B2 as compared to the NIRCam long wavelength filters with some overlap and that the F430M filter is the best match with the MSX bands.
Figure \ref{fig:msxNCfilterOverlap} also shows model spectra from \citet{castelli2004models} for the MSX calibrator stars in \citet{price2004msxCal} near these bandpasses.
The flux has been normalized for each star at 3.6~$\mu$m and then offset for clarity
We use the nearest match between the stellar types from the Simbad database and the suggested \citet{castelli2004models} parameters\footnote{http://www.stsci.edu/hst/observatory/crds/castelli\_kurucz\_atlas.html}.

>>>>

There are several ways to improve saturation limits with NIRCam over direct imaging:
\begin{itemize}
\item \textbf{Lyot Stop} Cut down the aperture size with a Lyot stop. These have 19\% throughput (1.8 mags). Additionally, this broadens the PSF - see Figure \ref{fig:psfComparison}.
The broadening spreads light out by a similar factor (1.8 mags) for a total of 3.5 mags.
\item \textbf{Neutral Density Square} The neutral density filters have an attenuation of around 10$^3$ or 7.5 mags. A color correction would have to be applied for the neutral density filter (since it is wavelength dependent) when transferring to an un-occulted region.
Additionally, the Lyot stop that must be in place to use the neutral density filter so the total improvement is 11 mags over direct imaging.
Care must be taken with dithering to ensure that non-uniform optical depth of the neutral density filter doesn't affect the photometry.
\item \textbf{Grisms} For long wavelength observations, one can use grism to spread out the light. This mode still has a saturation limit of $K$=4.6 to 3.5 for the F322W2  filter \citep{greene2016wfss}, which does not reach to the MSX standards. This could be potentially combined with the coronagraph, but both at once hasn't been explored much. One could potentially observe small pieces of the spectrum at a time with a subarray that moves along the spectrum, but this would likely be harder to implement.
\item \textbf{DHS} The dispersed Hartmann Sensor (DHS) reduces the pupil throughput and spreads the light out to reach saturation limits of $K$=0.2 to 1.5 depending on spectral type \citep{schlawin2017dhs}. This would also have to be read out with a moving subarray to observe the MSX stars.
\item Use a narrowband filter, such as F121N
\item Use a small subarray - 64 $\times$ 64 is supported for science. There will be an engineering jitter monitoring test with an 8 $\times$ 8 subarray 
\item \textbf{Weak Lens} The Weak Lenses spread light out over many pixels which can be helpful for bright stars. However, one needs to read out larger sized subarrays to encompass the entire hexagonal PSF so this somewhat cancels out.
\end{itemize}

Of the many options here, the most feasible method is the neutral density square with the Lyot Coronagraphic pupil mask.
Sensitivity and saturation limits make use of \texttt{pysynphot} \citep{lim2015pysynphot} with Phoenix stellar models \citep{allard2012phoenix} ranging from 4.0 to 5.0 in log(g).

@@

Figure \ref{fig:msxNCfilterOverlap} shows the MSX filters B1 and B2 as compared to the NIRCam long wavelength filters with some overlap and that the F430M filter is the best match with the MSX bands.
Figure \ref{fig:msxNCfilterOverlap} also shows model spectra from \citet{castelli2004models} for the MSX calibrator stars in \citet{price2004msxCal} near these bandpasses.
The flux has been normalized for each star at 3.6~$\mu$m and then offset for clarity.
We use the nearest match between the stellar types from the Simbad database and the suggested \citet{castelli2004models} parameters\footnote{http://www.stsci.edu/hst/observatory/crds/castelli\_kurucz\_atlas.html}.
